\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-09-25 docs/proposal/doc.tex
Rewrote part on functional connectivity.
wijzigingen aan causal discovery methods / strategy

\subsection*{Causal discovery methods}
The causal discovery method which we will use is the BCCD-algorithm. This algorithm finds both the structure of a network as well as the direction of the connections of this network. This algorithm has some useful properties; it is based on a Bayesian approach and as such, it is robust. It also does not need any assumptions beforehand. Because of this, the algorithm performs at least as good as other causal discovery algorithms such as FCI and PC in benchmarks on representative datasets, and in some cases it performs better. BCCD also finds the reliability of found connections, giving additional information compared to PC and FCI.

>>>>

\subsection*{Causal discovery methods}
The first causal method that we will use to find effective connectivity will be the PC-algorithm.
This is a state of the art used for general causal discovery, which finds the structure and the direction of connections of this network.
The structure of a network can also be given as input, for which the PC-algorithm can determine the directions.
Another causal discovery method is the BCCD-algorithm \cite{claassen2012}, which gives similar results as PC.
This algorithm has some useful properties; it is based on a Bayesian approach and as such, it is robust.
It also does not need any assumptions beforehand.
Because of this, the algorithm performs at least as good as other causal discovery algorithms such as FCI and PC in benchmarks on representative datasets, and in some cases it performs better.
BCCD also finds the reliability of found connections, giving additional information compared to PC and FCI.
